Beliefs about the development of mental life

### 2021-08-02 paper/paper.Rmd
update mind-mindedness

Adults’ intuitive theories are likely to have important consequences for the children in their care [@haimovitz.dweck2016; @hembacher.etal2020; @mukhopadhyay.yeung2010]. We suspect that intuitive theories of the development of mental life could play a particularly important role in the quality of caregiver–child relationships in the first few years of a child’s life. During this period, caregivers cannot rely on children to clearly communicate through words; instead, caregivers often must _infer_ what children think and feel. These inferences critically depend on the adult’s understanding of what the child is and is not capable of, and what scaffolding it would take for that child to become more capable. There is evidence of this across domains of development. For example, parent language use becomes more diverse and complex as children age and in concert with developing sophistication of the child’s own language competence [@rowe.etal2005; @huttenlocher.etal2010], and parents interact differently depending on whether a child is crawling versus walking [@karasik.etal2014] and holding versus looking at an object [@west.iverson2017]. Likewise, representations of children’s mental lives, including their sensations, perceptions, emotions, cognitive abilities, executive function, and social skills have been shown to play a critical role in guiding adults’ expectations of a child, their reactions to that child’s actions, and the nature and development of their relationship with the child [@vreeswijk.etal2012; @feldman.reznick1996].

>>>>

Adults’ intuitive theories are likely to have important consequences for the children in their care [@haimovitz.dweck2016; @hembacher.etal2020; @mukhopadhyay.yeung2010]. We suspect that intuitive theories of the development of mental life could play a particularly important role in the quality of caregiver–child relationships in the first few years of a child’s life. During this period, caregivers cannot rely on children to clearly communicate through words; instead, caregivers often must _infer_ what children think and feel. These inferences critically depend on the adult’s understanding of what the child is and is not capable of, and what scaffolding it would take for that child to become more capable. There is evidence of this across domains of development. For example, parent language use becomes more diverse and complex as children age and in concert with developing sophistication of the child’s own language competence [@rowe.etal2005; @huttenlocher.etal2010], and parents interact differently depending on whether a child is crawling versus walking [@karasik.etal2014] or holding versus looking at an object [@west.iverson2017]. Likewise, representations of children’s mental lives, including their sensations, perceptions, emotions, cognitive abilities, executive function, and social skills have been shown to play a critical role in guiding adults’ expectations of a child, their reactions to that child’s actions, and the nature and development of their relationship with the child [@vreeswijk.etal2012; @feldman.reznick1996]. Caregivers’ capacity to form an accurate representation of their child’s internal states and to use this representation to guide their caregiving behavior (so called “mind-mindedness”) is positively associated with children’s wellbeing, including attachment security, theory of mind, and ultimately, school readiness [@meins.etal2012; @meins.etal2013; @bernier.etal2017].
